---
title: "Using the rxy Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the rxy Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

# Ensure the package is loaded
library(rxy)
```

Introduction 

The rxy package provides tools for analyzing correlations
between a dependent variable and multiple independent variables. It also
includes methods for printing, plotting, and summarizing the results.

This vignette demonstrates how to use the package with the Boston
dataset from the MASS package.

Getting Started

Install and load the rxy package:
```{r}
# Install the package (if not already installed)
# devtools::install("path_to_rxy")
library(rxy)

```
Load the MASS package and use the Boston dataset:
```{r}
library(MASS)
data("Boston")

```

Analyze Correlations

Run the ryx function to analyze correlations between the dependent variable (medv) and independent variables:
```{r}
result <- ryx(Boston, y = "medv")
```

Print the Results

Use the print method to display the correlation results:
```{r}
print(result)
```

Plot the Results

Plotting the results with the plot method:
```{r}
plot(result)
```

Summarize the Results

Summarize the correlations with the summary method:
```{r}
summary(result)
```

Conclusion

The rxy package provides an intuitive way to explore relationships between a dependent variable and multiple independent variables. Its print, plot, and summary methods make it easy to interpret the results.

